---
title: Rubrica 1984-92
author: Vito Sestito
date: '1984-01-01'
slug: rubrica-1984-92
categories:
  - Rubriche
description: Rubriche dove i film venivano annotati in ordine alfabetico, con data di proiezione e distributore.
---


{{< image-gallery gallery_dir="/images/1984_01_01_rubrica_1984_92" >}}


```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(knitr)

# Dati IMDb
imdb <- read_csv(here("static/data/programmazione_imdb.csv")) %>% 
  select(const = Const, url = URL)

# Dati fonte
proiezioni_fonte <- read_csv(here("static/data/programmazione_agende.csv")) %>%
  select(const, date, title, source) %>%
  filter(str_detect(source, "Rubrica 1984-92")) %>%
  left_join(imdb, by = "const") %>%
  mutate(title = paste0("[", title, "](", url, ")"))
```


## 1984
### Gennaio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1984, lubridate::month(date) == 1) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Febbraio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1984, lubridate::month(date) == 2) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Marzo

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1984, lubridate::month(date) == 3) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Aprile

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1984, lubridate::month(date) == 4) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Settembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1984, lubridate::month(date) == 9) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Ottobre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1984, lubridate::month(date) == 10) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Novembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1984, lubridate::month(date) == 11) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Dicembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1984, lubridate::month(date) == 12) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

## 1985
### Gennaio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1985, lubridate::month(date) == 1) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Febbraio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1985, lubridate::month(date) == 2) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Marzo

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1985, lubridate::month(date) == 3) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Settembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1985, lubridate::month(date) == 9) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Ottobre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1985, lubridate::month(date) == 10) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Novembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1985, lubridate::month(date) == 11) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Dicembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1985, lubridate::month(date) == 12) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

## 1986
### Gennaio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 1) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Febbraio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 2) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Marzo

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 3) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Aprile

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 4) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Maggio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 5) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Giugno

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 6) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Settembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 9) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Ottobre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 10) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Novembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 11) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Dicembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1986, lubridate::month(date) == 12) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

## 1987
### Gennaio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 1) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Febbraio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 2) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Marzo

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 3) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Aprile

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 4) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Maggio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 5) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Giugno

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 6) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Agosto

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 8) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Settembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 9) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Ottobre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 10) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Novembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 11) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Dicembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1987, lubridate::month(date) == 12) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

## 1988
### Gennaio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1988, lubridate::month(date) == 1) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Febbraio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1988, lubridate::month(date) == 2) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Marzo

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1988, lubridate::month(date) == 3) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Aprile

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1988, lubridate::month(date) == 4) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Maggio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1988, lubridate::month(date) == 5) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Settembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1988, lubridate::month(date) == 9) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Ottobre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1988, lubridate::month(date) == 10) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Novembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1988, lubridate::month(date) == 11) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Dicembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1988, lubridate::month(date) == 12) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

## 1989
### Gennaio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1989, lubridate::month(date) == 1) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Febbraio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1989, lubridate::month(date) == 2) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Marzo

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1989, lubridate::month(date) == 3) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Aprile

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1989, lubridate::month(date) == 4) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Maggio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1989, lubridate::month(date) == 5) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Settembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1989, lubridate::month(date) == 9) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Ottobre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1989, lubridate::month(date) == 10) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Novembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1989, lubridate::month(date) == 11) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Dicembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1989, lubridate::month(date) == 12) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

## 1990
### Gennaio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1990, lubridate::month(date) == 1) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Febbraio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1990, lubridate::month(date) == 2) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Marzo

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1990, lubridate::month(date) == 3) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Aprile

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1990, lubridate::month(date) == 4) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Maggio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1990, lubridate::month(date) == 5) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Settembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1990, lubridate::month(date) == 9) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Ottobre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1990, lubridate::month(date) == 10) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Novembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1990, lubridate::month(date) == 11) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Dicembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1990, lubridate::month(date) == 12) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

## 1991
### Gennaio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 1) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Febbraio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 2) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Marzo

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 3) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Aprile

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 4) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Maggio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 5) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Giugno

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 6) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Settembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 9) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Ottobre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 10) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Novembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 11) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Dicembre

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1991, lubridate::month(date) == 12) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

## 1992
### Gennaio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1992, lubridate::month(date) == 1) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Febbraio

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1992, lubridate::month(date) == 2) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Marzo

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1992, lubridate::month(date) == 3) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```

### Aprile

```{r echo=FALSE}
library(knitr)
proiezioni_fonte %>% 
  filter(lubridate::year(date) == 1992, lubridate::month(date) == 4) %>% 
  select(date, title) %>% 
  arrange(date) %>% 
  kable(col.names = c("", ""))
```


